### 2019-02-16 manuscript/methods.tex
- minor changes (typos) noted at compilation - added ramanauskas2017 to replace igic2001

%B: we moved back from "SI" to "self-incompatibility" below. Maybe a no-no.
For all breeding system models, we allow transitions from $I$ to $C$ (at rate $q_{IC}$) but not the reverse. %B: was "these and the subsequent models including breeding systems"
Within Solanaceae, self-incompatibility is homologous in all species in which S-alleles were cloned, and controlled crosses performed.  
All species sampled to date, possess a non-self recognition, RNase-based, gametophytic self-incompatibility \citep[shared even shared even with other euasterid families;][]{ramanauskas2017}. %B: this now makes a narrower claim than igic_2001/steinbachs_2002, which includes Rosaceae and a bag of avoidable troubles. 
Furthermore, species that are distantly related within this family carry closely-related alleles, with deep trans-specific polymorphism, at the S-locus, which controls the SI response \citep{ioerger_1990, igic_2006}. %B: may need to introduce "S-locus" earlier.
This represents very strong evidence that the SI mechanism, and our $I$ state is ancestral to the Solanaceae, and did not arise independently within the family ($q_{CI}=0$). %B: I think I have this right <- someone please double-check.
% This is an important assumption because ancestral state reconstruction in the models might differ when polyploidy and breeding system are analyzed as independent in the Solanaceae tree.
% This irreversibility assumption prevents self-compatible state from evolving into self-incompatible state and as a result, the ancestral state of all taxa in this model has probability one of being self-incompatible.

@@

\begin{table}
\begin{tabular}{@{}llcccccc@{}} \toprule
%\multicolumn{4}{r}{Models} \\ \cmidrule(r){3-5}
Model& Model& Ploidy & Diploidization & Breeding  & Hidden & Parameters & Marginal \\
& Type & &  &System & State & & Log- Likelihood \\
1. D/P &BiSSE &	Yes  &	Yes &	No	&No	& 6	& -1182.93 \\
2. D/P no $\delta$ & BiSSE  &	Yes & 	No	& No	& No & 	5 &	-1193.66\\
3. D/P- A/B  & HiSSE &	Yes &	Yes	&No &	Yes &	11 &	\textbf{-1145.69}\\
4. D/P no $\delta$-A/B &	HiSSE &	Yes & No &	No &	Yes &	10	&-1150.99\\
5. I/C &	BiSSE &	No &	 No	&Yes &	No &	 5 &  -1194.80 \\
6. I/C-A/B &	HiSSE &	No &	 No	&Yes &	Yes	& 10 & \textbf{-1155.37}\\
7. ID/P/CD & MuSSE &	Yes & 	Yes &	Yes &	No &	10 & -1344.50\\
8. ID/P/CD no $\delta$ &	MuSSE &	Yes & 	No &	Yes	&No &	9 &-1345.87\\
9. ID/P/CD-A/B & MuHiSSE &	Yes 	&Yes &	Yes &	Yes &	16 & \textbf{-1300.35} \\
10.ID/P/CD no $\delta$-A/B &	 MuHiSSE	 & Yes & 	No	&Yes &	Yes	&15 &-1303.55 \\ \bottomrule
\end{tabular}
\caption{Marginal likelihoods for the 10 diversification models proposed.}
\label{table:marginallike}
\end{table}

\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|c|c|c|}
\toprule
Polyploidy Models & Breeding System Models & Polyploidy and Breeding System Models \\ \midrule
{\begin{tabular}{lcccc}
 & 1 & 2 & 3 & 4 \\
1. D/P & $\cdot$	 &10.72 &	-37.24	&-31.94\\
2. D/P no $\delta$ &$\cdot$&$\cdot$ &	-47.97	&-42.66\\
\textbf{3. D/P- A/B}  &$\cdot$  & $\cdot$&	$\cdot$	& 5.30 \\
4. D/P no $\delta$-A/B &$\cdot$& $\cdot$ & $\cdot$&$\cdot$ \\
\end{tabular}
}  & 
{\begin{tabular}{lcc}
 & 5 & 6\\
5. I/C &$\cdot$ & -39.43 \\
\textbf{6. I/C-A/B} &$\cdot$& $\cdot$ \\
& & \\
& & \\
\end{tabular}
} & 
{\begin{tabular}{lcccc}
& 7 & 8 & 9 & 10\\
7. ID/P/CD & $\cdot$	&1.36 & -44.15&-40.95 \\
8. ID/P/CD no $\delta$ & $\cdot$ & $\cdot$ & -45.51 &-42.31 \\
\textbf{9. ID/P/CD-A/B}& $\cdot$ & $\cdot$ &$\cdot$	& 3.2 \\ 
10. ID/P/CD no $\delta$-A/B & $\cdot$& $\cdot$&$\cdot$ & $\cdot$\\
\end{tabular}
}\\
\bottomrule
\end{tabular}
 \caption{Bayes factors in log scale. We compare every possible pair. Number models as indicated in  \cref{table:marginallike}. }
\label{table:bayesfactors}
\end{table}

>>>>

%B: we moved back from "SI" to "self-incompatibility" below. Maybe a no-no.
For all breeding system models, we allow transitions from $I$ to $C$ (at rate $q_{IC}$) but not the reverse. %B: was "these and the subsequent models including breeding systems"
Within Solanaceae, self-incompatibility is homologous in all species in which S-alleles were cloned, and controlled crosses performed.  
All species sampled to date, possess a non-self recognition, RNase-based, gametophytic self-incompatibility \citep[shared even shared even with other euasterid families;][]{ramanauskas_2017}. %B: this now makes a narrower claim than igic_2001/steinbachs_2002, which includes Rosaceae and a bag of avoidable troubles. 
Furthermore, species that are distantly related within this family carry closely-related alleles, with deep trans-specific polymorphism, at the S-locus, which controls the SI response \citep{ioerger_1990, igic_2006}. %B: may need to introduce "S-locus" earlier.
This represents very strong evidence that the SI mechanism, and our $I$ state is ancestral to the Solanaceae, and did not arise independently within the family ($q_{CI}=0$). %B: I think I have this right <- someone please double-check.
% This is an important assumption because ancestral state reconstruction in the models might differ when polyploidy and breeding system are analyzed as independent in the Solanaceae tree.
% This irreversibility assumption prevents self-compatible state from evolving into self-incompatible state and as a result, the ancestral state of all taxa in this model has probability one of being self-incompatible.

@@

\begin{table}
\begin{tabular}{@{}llcccccc@{}} \toprule
%\multicolumn{4}{r}{Models} \\ \cmidrule(r){3-5}
Model& Model& Ploidy & Diploidization & Breeding  & Hidden & Parameters & Marginal \\
& Type & &  &System & State & & Log- Likelihood \\
1. D/P &BiSSE &	Yes  &	Yes &	No	&No	& 6	& -1182.93 \\
2. D/P no $\delta$ & BiSSE  &	Yes & 	No	& No	& No & 	5 &	-1193.66\\
3. D/P- A/B  & HiSSE &	Yes &	Yes	&No &	Yes &	11 &	\textbf{-1145.69}\\
4. D/P no $\delta$-A/B &	HiSSE &	Yes & No &	No &	Yes &	10	&-1150.99\\
5. I/C &	BiSSE &	No &	 No	&Yes &	No &	 5 &  -1194.80 \\
6. I/C-A/B &	HiSSE &	No &	 No	&Yes &	Yes	& 10 & \textbf{-1155.37}\\
7. ID/P/CD & MuSSE &	Yes & 	Yes &	Yes &	No &	10 & -1344.50\\
8. ID/P/CD no $\delta$ &	MuSSE &	Yes & 	No &	Yes	&No &	9 &-1345.87\\
9. ID/P/CD-A/B & MuHiSSE &	Yes 	&Yes &	Yes &	Yes &	16 & \textbf{-1300.35} \\
10.ID/P/CD no $\delta$-A/B &	 MuHiSSE	 & Yes & 	No	&Yes &	Yes	&15 &-1303.55 \\ \bottomrule
\end{tabular}
\caption{Marginal likelihoods for the ten models examined. States encoded with letter D: diploid, P: polyploid, C: self-compatible, I: self-incompatible, A: first state of hidden trait, B: second state of hidden trait, $\delta$: re-diploidization.}
\label{table:marginallike}
\end{table}

\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|c|c|c|}
\toprule
Ploidy Models & Breeding System Models & Ploidy and Breeding System Models \\ \midrule
{\begin{tabular}{lcccc}
 & 1 & 2 & 3 & 4 \\
1. D/P & $\cdot$	 &10.72 &	-37.24	&-31.94\\
2. D/P no $\delta$ &$\cdot$&$\cdot$ &	-47.97	&-42.66\\
\textbf{3. D/P- A/B}  &$\cdot$  & $\cdot$&	$\cdot$	& 5.30 \\
4. D/P no $\delta$-A/B &$\cdot$& $\cdot$ & $\cdot$&$\cdot$ \\
\end{tabular}
}  & 
{\begin{tabular}{lcc}
 & 5 & 6\\
5. I/C &$\cdot$ & -39.43 \\
\textbf{6. I/C-A/B} &$\cdot$& $\cdot$ \\
& & \\
& & \\
\end{tabular}
} & 
{\begin{tabular}{lcccc}
& 7 & 8 & 9 & 10\\
7. ID/P/CD & $\cdot$	&1.36 & -44.15&-40.95 \\
8. ID/P/CD no $\delta$ & $\cdot$ & $\cdot$ & -45.51 &-42.31 \\
\textbf{9. ID/P/CD-A/B}& $\cdot$ & $\cdot$ &$\cdot$	& 3.2 \\ 
10. ID/P/CD no $\delta$-A/B & $\cdot$& $\cdot$&$\cdot$ & $\cdot$\\
\end{tabular}
}\\
\bottomrule
\end{tabular}
 \caption{Bayes factors in log scale. We compare every possible pair. Number models as indicated in  \cref{table:marginallike}. }
\label{table:bayesfactors}
\end{table}
